### 2024-12-10 README.Rmd

Here's our basemap via `geodata`:
```{r}
#install.packages("geodata")
library(geodata)
sin <- gadm(
  country = "Singapore",
  level = 0,
  path = tempdir(),
  resolution = 2
)
plot(sin)
```

>>>>

Here's our basemap via `geodata`:

```{r}
#install.packages("geodata")
library(geodata)
sin <- gadm(
  country = "Singapore",
  level = 0,
  path = tempdir(),
  resolution = 2
)
plot(sin)
```
